Leaf traits drive differences in biomass partitioning among major plant functional types

### 2015-01-13 manuscript.Rnw
Figure 4 has 3 regression lines in panel a

<<echo=FALSE>>=
agg <- summaryBy(lalf_astba2 + lmlf_astba2 + llma ~ Group,
                   data=dataset, FUN=mean, na.rm=TRUE, keep.names=TRUE,
                   id=~pft)
agg <- subset(agg, !is.na(llma))
lm1 <- lm(lmlf_astba2 ~ llma, data=agg)
lm2 <- lm(lmlf_astba2 ~ lalf_astba2 * pft, data=agg)
r2panela <- summary(lm1)$adj.r.squared
r2panelb <- summary(lm2)$adj.r.squared
@

>>>>

<<echo=FALSE>>=
agg <- summaryBy(lalf_astba2 + lmlf_astba2 + llma ~ Group,
                   data=dataset, FUN=mean, na.rm=TRUE, keep.names=TRUE,
                   id=~pft)
agg <- subset(agg, !is.na(llma))
lm1 <- lm(lmlf_astba2 ~ llma * pft, data=agg)
lm2 <- lm(lmlf_astba2 ~ lalf_astba2 * pft, data=agg)
r2panela <- summary(lm1)$adj.r.squared
r2panelb <- summary(lm2)$adj.r.squared
@
